Gov 50 Final Project

### 2022-12-08 article.Rmd
final

```{r}
install.packages("broom")
library(tidy)
```

@@

```
Average support for opening houses of worship is negative 0.488 when the main explanatory variable (Party affiliation) is zero. This means, when a particular respondent is not a Republican their predicted support for opening houses of worship is negative and it can be predicted that they would want places of worship to remain closed, given all else remains constant.

@@

modelsummary::modelsummary(list(sing_Regression, Mult_regression), gof_map("nobs"))
```

@@

For the coefficients, since all the explanatory variables used here are binary, our model predicts that if a person goes from being a non-Republican (in this case a Democrat) to a Republican, their predicted support for opening up places of worship during the pandemic would increase by 0.51 points, given all else remains constant. This means that on average becoming a republican is predicted to be associated with a rise in support for opening places of worship, given all other variables remain unchanged. 
Similarly, being a black person is associated with a decrease in the predicted support for the opening of places of worship by 0.019 points, given all other variables remain constant. 
Being a college graduate is associated with a decrease in the predicted support for the opening of places of worship by 0.14 points, given all other variables remain constant. 
And lastly, being someone who engages in some form of spiritual practice (prayer, reading scripture, meditation) is associated with an increase in the predicted support for the opening of places of worship by 0.0021, given all other variables remain constant.

>>>>

```{r}
library(broom)
library(tidyr)
```

@@

var_labs <- c("(Intercept)" = "Intercept", "PARTY_affiliationRepublican" = "Republican Party")
modelsummary::modelsummary(list(sing_Regression), coef_map = var_labs, gof_map= ("nobs"))
```
Average support for opening houses of worship is negative 0.488 when the main explanatory variable (Party affiliation) is zero. This means, when a particular respondent is not a Republican their predicted support for opening houses of worship is negative and it can be predicted that they would want places of worship to remain closed, given all else remains constant.

@@

var_labels <- c( "(Intercept)" = "Intercept", "PARTY_affiliationRepublican" = "Republican Party", "Black1" = "Black", "ColEducation_binary1" = "College graduate", "spirtuality1" = "Spirituality")

modelsummary::modelsummary(list(sing_Regression, Mult_regression), coef_map = var_labels, gof_map= ("nobs"))
```

@@

For the coefficients, since all the explanatory variables used here are binary, our model predicts that if a person goes from being a non-Republican (in this case a Democrat) to a Republican, their predicted support for opening up places of worship during the pandemic would increase by 0.514 points, given all else remains constant. This means that on average becoming a republican is predicted to be associated with a rise in support for opening places of worship, given all other variables remain unchanged. 
Similarly, being a black person is associated with a decrease in the predicted support for the opening of places of worship by 0.02 points, given all other variables remain constant. 
Being a college graduate is associated with a decrease in the predicted support for the opening of places of worship by 0.14 points, given all other variables remain constant. 
And lastly, being someone who engages in some form of spiritual practice (prayer, reading scripture, meditation) is associated with an increase in the predicted support for the opening of places of worship by 0.002, given all other variables remain constant.
